\cvsection{Experiences}
\begin{cventries}
  \cventry
    {Freelance Software Engineer}
    {Freelance}
    {Brooklyn, NY}
    {Mar 2017 - Present}
    {
      \begin{cvitems}
        \item {Working on a range of freelance web projects using Amazon web services, Mailchimp and Wordpress.}
         \item {Discuss options with clients to make sure websites meet their needs as well as the needs of their customers.}
          \item {Managed websites and design/creation for clients around the country.}
           \item {Maintained and updated customer websites as needed.}
      \end{cvitems}
    }
  \cventry
    {Teacher at Lyons Community School}
    {Scripted}
    {Brooklyn, NY}
    {Mar 2017 - Present}
    {
      \begin{cvitems}
        \item {Teach fundamentals of HTML, CSS and JavaScript to high school students in under resourced schools.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Bounce Exchange}
    {New York, NY}
    {Jan 2016 - Mar 2017}
    {
      \begin{cvitems}
        \item {Performed client-side integrations with Bounce Exchange behavior automation platform using Vanilla JavaScript and jQuery.}
        \item{Collaborated with design and accounts to deliver custom campaigns across many high traffic e-commerce and publisher sites.}
        \item{Integrated numerous Web Services and APIs with a primary focus on Email Service Providers using PHP CodeIgniter and JavaScript.}
        \begin{itemize}[leftmargin=5.5mm]
            \item[\bullet] {Developed in-house APIs for SendGrid, Mailchimp, Bronto, Salesforce, Experian, Uniqlo and many more.}
        \end{itemize}
        \item{Assisted in rolling out client-side side V2 inbox retargeting engine.}
        \begin{itemize}[leftmargin=5.5mm]
            \item[\bullet]{Built JavaScript tracking boiler-plates leading to a decrease in complexity, client roll-out and bugs.} 
        \end{itemize}
        \item{Worked alongside accounts and analytics to create experimental campaigns and platform features.}
        \item{Managed Bouncex homepage, working closely with design lead on site changes.}
        \begin{itemize}[leftmargin=5.5mm]
        \item[\bullet]{Implemented Facebook and google conversion tracking.}
        \end{itemize}
        \item{Paired programmed and helped onboard new engineers with the platform and codebase.}
      \end{cvitems}
    }
  \cventry
    {DIIT IPDVS Engineer Intern}
    {Department of Education }
    {Brooklyn, NY}
    {Mar 2015 - July 2015}
    {
      \begin{cvitems}
        \item {Created a script in Java that automated inspections of more than 500 DOE sites, providing diagnostics and detailed reporting.}
        \item{Performed full site assessments at DOE schools, including technical reports and documentation.}
      \end{cvitems}
    }
\end{cventries}
